Conversations in Time: Interactive Visualization to Explore Structured Temporal Data

### 2021-08-09 rjdistill_version/tsibbletalk.Rmd
reduced size of main interactive plot and fixed label locations
updates to distill version

```{r tourism-multi, echo = TRUE, eval = knitr::is_html_output(), fig.cap = "Exploring an ensemble of linked plots of the Australian tourism data, built on a \\code{tourism\\_shared} object. Click one of the nodes in the hierarchical tree to enable persistent linked brushing to compare two groups. Points and lines can also be selected in other plots."}
```

>>>>

```{r tourism-multi, layout="l-body-outset", echo = TRUE, eval = knitr::is_html_output(), fig.cap = "Exploring an ensemble of linked plots of the Australian tourism data, built on a \\code{tourism\\_shared} object. Click one of the nodes in the hierarchical tree to enable persistent linked brushing to compare two groups. Points and lines can also be selected in other plots. (Only Western Australia and Tasmania are included for the interactive plot in the html version, so size reasons.)"}
```
